Notebook

### 2022-03-04 doc/notebook/notebook.Rmd
Change size of frog length:weight plot

```{r, fig.width = 3, fig.align = "center"}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = lm)
```

>>>>

```{r, fig.width = 6, fig.align = "center"}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = lm)
plot
```
